Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-28 report/report.tex
Update todo
Update collision statistics table

% TODO: Collision correction run (Enter data in report)
% TODO: Figure of street, before correction, after correction

% LARGE DATA RUN
% TODO: Start large data run, way collision
% TODO: Enter for correction data in report

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 1391          & 256          & 107         & 148         \\
    Nodes, total            & 264179        & 26771        & 6997        & 10686       \\
    Edge length, total      & 5004997.34 m  & 814349.47 m  & 169129.19 m & 307461.81 m \\
    Features, colliding     & 141           & 24           & 20          & 22          \\
    Nodes, colliding        & 302           & 48           & 38          & 42          \\
    Edge length, colliding  & 7779.66 m     & 1197.50 m    & 1074.88 m   & 1291.26 m   \\
    Features, percent       & 10.13 \%      & 9.38 \%      & 18.69 \%    & 14.86 \%    \\
    Nodes, percent          & 0.11 \%       & 0.18 \%      & 0.54 \%     & 0.39 \%     \\
    Edge length, percent    & 0.015 \%      & 0.15 \%      & 0.64 \%     & 0.42 \%

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, colliding     & 1             & 0            & 2           & 0           \\
    Nodes, colliding        & 1             & 0            & 2           & 0           \\
    Edge length, colliding  & 4.20 m        & 0.00 m       & 17.67 m     & 0.00 m      \\
    Features, percent       & 0.07 \%       & 0.00 \%      & 1.87 \%     & 0.00 \%     \\
    Nodes, percent          & 0.00 \%       & 0.00 \%      & 0.02 \%     & 0.00 \%     \\
    Edge length, percent    & 0.00 \%       & 0.00 \%      & 0.01 \%     & 0.00 \%

>>>>

% REPORT
% TODO: Enter correction data in report
% TODO: Analysis, write about the building-road case
% TODO: Analysis, write about the road-road case
% TODO: Plot features before collision, building-road
% TODO: Plot features before collision, road-road
% TODO: Proposed fixing algorithm: building-road
% TODO: Proposed fixing algorithm: road-road
% TODO: Analysis, mention that footpaths were nor worse than other categories, which are included in many unity packages already
% TODO: Figure, suggested morphing, building-road case
% TODO: Figure, suggested morphing, road-road case
% TODO: Proof read report

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 26473         & 10523        & 3044        & 2756        \\
    Nodes, total            & 6382579       & 6612383      & 968420      & 420810      \\
    Edge length, total      & 129984.79 km  & 186089.55 km & 29304.57 km & 16162.95 km \\
    Features, colliding     & 3189          & 1032         & 412         & 456         \\
    Nodes, colliding        & 7330          & 2362         & 643         & 824         \\
    Edge length, colliding  & 110.67 km     & 66.18 km     & 9389.30 m   & 20.41 km    \\
    Features, percent       & 12.05 \%      & 9.81 \%      & 13.53 \%    & 16.55 \%    \\
    Nodes, percent          & 0.11 \%       & 0.04 \%      & 0.07 \%     & 0.20 \%     \\
    Edge length, percent    & 0.09 \%       & 0.04 \%      & 0.03 \%     & 0133 \%

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, colliding     & 134           & 336          & 246         & 277         \\
    Nodes, colliding        & 157           & 530          & 306         & 407         \\
    Edge length, colliding  & 3248.73       & 6475.99 m    & 3840.00 m   & 8039.54 m   \\
    Features, percent       & 0.51 \%       & 3.19 \%      & 8.08 \%     & 10.51 \%    \\
    Nodes, percent          & 0.00 \%       & 0.00 \%      & 0.03 \%     & 0.09 \%     \\
    Edge length, percent    & 0.00 \%       & 0.00 \%      & 0.01 \%     & 0.05 \%
